\begin{abstract}
Machine unlearning---removing specific data from trained models without full
retraining---is increasingly mandated by privacy regulation and routinely
deployed in graph learning systems where deletion requests target individual
nodes or edges. \emph{Approximate} graph unlearning (GU) methods trade exact
removal for orders-of-magnitude speedup, but the resulting approximation gap
is, we show, \emph{adversarially exploitable} by an attacker who controls
the deletion set.

We present, to our knowledge, the first systematic adversarial audit of
approximate GU. The attacker selects a small set of nodes to forcibly
unlearn---via influence-maximization, pseudo-influence functions, or hybrid
strategies---aiming to amplify approximation error and collapse downstream
utility. We evaluate \textbf{six} representative methods covering three of
the four upstream OpenGU categories with \emph{intra-family pairs} in each:
Partition-based (GraphEraser, GraphRevoker), Influence-Function-based
(GIF, IDEA), and Learning-based (GNNDelete, MEGU). Experiments span Cora,
Citeseer, and ogbn-arxiv (169K nodes) with GCN and GAT backbones.

Our findings reveal a stark \textbf{Vulnerability Fingerprint}---a 2D
geometry whose axes are the structural-spread (IM) and gradient-signal
(TracIn) attack-specific F1 effects:
(i)~Learning-based \textbf{GNNDelete} collapses by an average of
\interim{16\%} F1 with peaks above \interim{27\%} under a deletion budget
below 5\% of training nodes;
(ii)~IF-based \textbf{GIF} shows a small but statistically significant
vulnerability (paired effect $\approx$\interim{+4\%} F1,
$p$\interim{$<$0.001}) bounded by its Newton-step approximation;
(iii)~the Partition family exhibits a counterintuitive \textbf{Shard
Protection Effect}---random and adversarial deletion both \emph{improve}
downstream F1 by \interim{3--6\%}, formally an \emph{architectural}
F1-shift term $\Delta F_{\text{arch}}<0$ that no selector can amplify;
(iv)~the \textbf{intra-family outliers} MEGU (Learning-based,
mutual-evolution) and IDEA (IF-based, certified-gradient) exhibit null
effect ($<$\interim{1\%} F1 difference) despite belonging to vulnerable
parent categories, revealing within-family heterogeneity that current
gradient/diffusion-based selectors cannot exploit.

We further introduce a \textbf{collateral diagnostics} suite---an explicit
$\Delta F_{\text{total}}=\Delta F_{\text{arch}}+\Delta F_{\text{attack}}$
decomposition, retrain gap, prediction shift, and a novel
\textbf{hop-distance decay} metric quantifying disturbance propagation
through the GNN's receptive field---providing a principled audit kit for
any future approximate-GU deployment.
\end{abstract}
