\section{Introduction}
\label{sec:intro}

Machine unlearning is no longer optional. Privacy regulations
(GDPR Art.\ 17, CCPA \S1798.105, EU AI Act) grant data subjects the right
to request removal of their data from trained models, and graph learning
systems---recommendation, fraud detection, citation analysis,
knowledge-graph-augmented retrieval---are squarely in scope.
The naive solution is retrain-from-scratch, but for production GNNs over
million-node graphs this is computationally prohibitive. \emph{Approximate
graph unlearning} (GU) methods~\cite{chen2022graph,wu2023gif,cheng2023gnndelete,li2024towards,dong2024idea,zhang2024towards}
trade exact removal for orders-of-magnitude speedup by performing
gradient-, influence-, or partition-based local updates.

This trade-off is justified under the implicit assumption that deletion
requests are \emph{benign}---i.e., independent of the model. In adversarial
settings this assumption fails. An adversary who controls even a small
fraction of deletion requests (e.g., a coalition of users on a platform
that honors deletion-by-API) can choose \emph{which} data to forcibly
remove. We show that this single degree of freedom---selecting the
deletion set---is sufficient to collapse the utility of widely-deployed
approximate GU methods, while leaving a second class of methods
\emph{within the same families} effectively untouched.

\paragraph{This paper.}
We conduct the first systematic adversarial audit of approximate GU,
treating deletion-set selection as the attacker's strategy and
post-unlearning downstream F1 as the victim's utility. To audit each
mechanism family fairly, we test \textbf{intra-family pairs} drawn from the
upstream OpenGU 4-category taxonomy: a canonical method and a method
predicted to be either convergent or an outlier. Our contributions are:

\begin{itemize}[leftmargin=1.2em,topsep=2pt,itemsep=2pt]
  \item \textbf{Threat model and four-tier access spectrum}
        (\S\ref{sec:method}). We formalize \emph{adversarial deletion
        attacks} on GU and refine the usual black/grey/white distinction
        into four tiers keyed on \emph{resource cost}: deletion API only
        (L0), structural-only (L1, free under coalition-of-users),
        model-coupled with production weights (L2-direct, the upper
        bound), and model-coupled via shadow-model surrogate
        (L2-surrogate, the realistic threat). We instantiate six
        selection strategies---a TracIn pseudo-IF score (L2-direct),
        a CELF-style influence-maximization (IM) selector (L1,
        model-free), and a hybrid IF$+$IM combination whose mixing
        parameter $\alpha$ defines the basis axes of our headline figure.
  \item \textbf{Vulnerability Fingerprint} (\S\ref{sec:results}). We
        introduce a 2D mechanism decomposition---attack effects projected
        on the IM and TracIn axes---and benchmark six GU methods covering
        three OpenGU categories (Partition, IF, Learning) on Cora,
        Citeseer, and ogbn-arxiv with GCN/GAT backbones. The fingerprint
        reveals that vulnerability is governed by the \emph{algorithm
        family}, modulated by within-family mechanism choice.
  \item \textbf{Collateral diagnostics with $\Delta F$ decomposition.} We
        introduce $\Delta F_{\text{total}}=\Delta F_{\text{arch}}+\Delta
        F_{\text{attack}}$, an explicit separation of attack-specific
        signal from the architectural F1 shift induced by deleting
        \emph{any} small set, and complementary metrics: retrain gap,
        prediction shift, and a novel \emph{hop-distance decay} statistic
        that traces how unlearning propagates through the GNN's receptive
        field.
  \item \textbf{Shard Protection Effect.} We document and explain a
        counterintuitive phenomenon: shard-based unlearning (GraphEraser,
        GraphRevoker) is not merely robust but \emph{benefits} from
        deletion---random and adversarial deletion both improve downstream
        F1, with the attacker's gain bounded above by random selection.
        The decomposition above lets us attribute this cleanly to
        $\Delta F_{\text{arch}}<0$, not to attack-specific signal.
  \item \textbf{Intra-family outliers.} We identify two methods---MEGU
        (Learning-based, mutual-evolution) and IDEA (IF-based,
        certified-gradient)---on which all six attack strategies including
        model-coupled influence functions fail to produce a meaningful
        effect, even though their family-mates (GNNDelete, GIF) are
        clearly vulnerable. We frame this as within-family heterogeneity
        rather than family-level robustness, and discuss the implication
        that current selectors are decoupled from the algebraic
        structures of certified or mutual-information-based unlearners.
\end{itemize}

\paragraph{Why this matters now.}
Three factors converge. First, GU is moving from research code to
production: the past two years have seen at least five competitive
approximate methods benchmarked on
ogbn-scale~\cite{wu2023gif,cheng2023gnndelete,dong2024idea,li2024towards,zhang2024towards}.
Second, regulators are mandating deletion APIs at the same time. Third,
the GNN community has not yet stress-tested these methods against
\emph{adversarial} deletion---only random or uniform settings. Our work
closes that gap and provides a principled diagnostic kit
(\S\ref{sec:method}) that any future GU paper can use to report
vulnerability upper-bounds alongside efficiency.
