\section{Related Work}
\label{sec:related}

\paragraph{Approximate graph unlearning.}
We adopt the upstream \emph{OpenGU} 4-category taxonomy. \emph{Partition-based}
methods partition the graph into disjoint shards, train a sub-model per
shard, and aggregate at inference; deletion only retrains the affected
shard (GraphEraser~\cite{chen2022graph}, GUIDE, GraphRevoker), echoing
the SISA~\cite{bourtoule2021machine} sharded-retraining design from
non-graph unlearning.
\emph{Influence-Function-based} methods estimate the leave-one-out parameter
delta in closed form and apply a single Newton or proximal step
(GIF~\cite{wu2023gif}, CEU, CGU, GST, IDEA~\cite{dong2024idea}---certified
variant). \emph{Learning-based} methods retrain selectively over a
deletion-aware objective (GNNDelete~\cite{cheng2023gnndelete}, GUKD,
Projector, MEGU~\cite{li2024towards}---mutual-evolution variant, ScaleGUN,
D2DGN, SGU). A fourth ``Others'' category (UtU, Projector at deployment
time) is outside our scope. All methods above are evaluated under
\emph{random} deletion sets in the literature; we are unaware of prior
work that audits them under adversarial deletion-set selection. Our
\emph{intra-family pairing} design---one canonical method plus one
predicted-outlier per category---tests within-family vulnerability
heterogeneity, which the existing literature has not surfaced.

\paragraph{Adversarial machine unlearning.}
The closest line of work studies poisoning of unlearning requests for
\emph{tabular} models~\cite{marchant2022hard,di2022hidden}, where the
attacker crafts samples or selects deletion sets to slow down or
destabilize retraining. Camouflaged data
poisoning~\cite{di2022hidden} demonstrates that hidden trigger injection
can survive unlearning. None of these methods are directly applicable to
graph data, where structural dependence between training points violates
the i.i.d.\ assumptions underlying their analysis. Concurrent vision-domain
work~\cite{huang2024exploring} probes unlearning of classifiers but does
not consider graph structure.

\paragraph{Influence functions and influence maximization on graphs.}
Influence-function approximations for deep
models~\cite{koh2017understanding} have been extended to GNNs
(GIF~\cite{wu2023gif}, GST). TracIn~\cite{pruthi2020estimating} provides a
checkpoint-based, gradient-only proxy that avoids the Hessian inversion
cost. Influence maximization (IM) on networks is a classical
problem~\cite{kempe2003maximizing}; CELF~\cite{leskovec2007cost} and
CELF++~\cite{goyal2011celf++} are submodular acceleration heuristics. We
adapt IM as an attack-side selector under independent-cascade simulation,
with a decoupled Monte-Carlo seed (\S\ref{sec:method}) for cross-seed
reproducibility, and treat the IM/TracIn pair as the basis axes of our
Vulnerability Fingerprint.

\paragraph{Membership inference and model auditing.}
MIA against GNNs~\cite{olatunji2021membership,he2021stealing} provides a
related privacy-audit lens. The metric we report in
\S\ref{sec:results-mia}, however, is not a Shokri/Olatunji-style
shadow-model MIA. It is a method-native update-detection AUC inherited
from the OpenGU evaluation protocol: a posterior-shift
deletion-membership audit that scores whether requested-for-unlearning
nodes are more visible than held-out test nodes after an update. The
utility-collapse attacks we study are orthogonal to this audit but share
the deletion-API setting, and the two diagnostics decouple in our
results.
