\section{Attack Framework}
\label{sec:method}

\subsection{Threat Model and Access Spectrum}
\label{sec:threat-model}

We consider a graph $G=(V,E,X)$ with node features
$X\in\mathbb{R}^{|V|\times d}$, node labels $Y$, and a GNN classifier
$f_\theta$ trained on training mask
$\mathcal{D}_{\mathrm{tr}}\subset V$. A graph unlearning algorithm
$\mathcal{U}(f_\theta,\mathcal{D}_{\mathrm{tr}},S)\to f_{\theta'}$ takes a
deletion set $S\subset\mathcal{D}_{\mathrm{tr}}$ and returns an updated
model approximating retrain-from-scratch on
$\mathcal{D}_{\mathrm{tr}}\setminus S$.

\paragraph{Attacker capabilities.}
The attacker controls a deletion budget of
$k=\lceil r\cdot|\mathcal{D}_{\mathrm{tr}}|\rceil$ nodes, where $r$ is the
deletion ratio (we focus on $r=0.05$; \S\ref{app:ratio} reports the sweep).
The attacker selects $S\subset\mathcal{D}_{\mathrm{tr}}$ subject to
$|S|\le k$. Realistic deletion-API platforms motivate a
\emph{coalition-of-users} threat model: the attacker is a set of users who
jointly choose which records to forget. We do not assume the attacker can
modify training data or the unlearning algorithm itself.

\paragraph{Access spectrum.}
Selectors differ substantially in what information they need, and a
two-tier black/grey/white split obscures this. We use a finer, four-tier
spectrum (Table~\ref{tab:access}) keyed on \emph{resource cost}, not on
``which API endpoint is exposed''. Two observations sharpen the
realistic-threat reading:

\textit{(i)~Training-mask reconstruction is free.} Because
unlearning operates on training data, any user issuing a deletion
request necessarily knows that her own data is in
$\mathcal{D}_{\mathrm{tr}}$. A coalition of users joins these
memberships and reconstructs (most of) the training mask at cost $0$.
Combined with the public graph $G$, this gives the attacker the
\emph{structural-only} (L1) tier essentially for free.

\textit{(ii)~Model access is replaceable by surrogate training.} The
TracIn-style signals do not require the production model itself: an
attacker who knows the (commonly disclosed) training protocol can
train her own \emph{shadow model} on the reconstructed mask, run TracIn
on the shadow, and transfer the resulting deletion set
(see~\cite{papernot2017practical,demontis2019adversarial} for the
analogous pattern in adversarial examples). This converts
``model-coupled (L2) access'' from a permission question to a
\emph{GPU-hour} question. We split L2 accordingly:
L2-\textsc{direct} (production weights leaked, what we report) is an
\emph{upper bound} on L2-\textsc{surrogate} (shadow-model attack, the
realistic threat); the gap between the two is the cross-model
transferability of the selector and is left as future work
(\S\ref{sec:limitations}). White-box (L3) attackers who modify training
data or the unlearning algorithm are out of scope as they do not
correspond to a deletion-API threat.

\begin{table}[h]
\centering
\small
\caption{\textbf{Four-tier access spectrum for selection strategies.}
Cost is the resource an attacker spends \emph{after} obtaining a
deletion API. Coalition-of-users on a deletion-API platform plausibly
reaches L1 at cost $0$ and L2-\textsc{surrogate} at cost equal to one
shadow-model training run.}
\label{tab:access}
\begin{tabular}{@{}lllc@{}}
\toprule
Tier & Information available & Cost & Strategies \\
\midrule
L0 \emph{(deletion API only)}      & request $S\subset\mathcal{D}_{\mathrm{tr}}$              & $0$               & \textsc{Random} \\
L1 \emph{(structural)}             & + public $G=(V,E)$, training mask                          & $0$ (coalition)   & \textsc{Degree}, \textsc{PageRank}, \textsc{IM} \\
L2-\textsc{direct} \emph{(model)}  & + production $f_\theta$, gradients, checkpoints           & internal leak     & \textsc{TracIn}, \textsc{Hybrid} \emph{(upper bound)} \\
L2-\textsc{surrogate}              & + train shadow $\hat f_{\hat\theta}$ from public protocol & GPU-h             & \textsc{TracIn}, \textsc{Hybrid} \emph{(realistic)} \\
L3 \emph{(white-box)}              & + modify training data / algorithm                        & internal access   & \emph{out of scope} \\
\bottomrule
\end{tabular}
\end{table}

The two tiers we report on the fingerprint axes (\S\ref{sec:results-fingerprint})
are L1 (the IM axis) and L2-\textsc{direct} (the TracIn axis); the
L2-\textsc{surrogate} reading is bounded above by the L2-\textsc{direct}
numbers we report.

\paragraph{Attacker objective.}
Let $L(f;V_{\mathrm{te}})$ be downstream test F1 on the held-out test
set. The attacker maximizes the performance drop:
\begin{equation}
\label{eq:attacker-objective}
S^* = \argmax_{S\subset\mathcal{D}_{\mathrm{tr}},\,|S|\le k}\;
      L(f_\theta;V_{\mathrm{te}})
      - L\bigl(\mathcal{U}(f_\theta,\mathcal{D}_{\mathrm{tr}},S);V_{\mathrm{te}}\bigr).
\end{equation}
Because $\mathcal{U}$ is approximate, the gap between
$\mathcal{U}(f_\theta,\cdot,S)$ and the exact retrain on
$\mathcal{D}_{\mathrm{tr}}\setminus S$ is non-zero, and the attacker's
task is to find $S$ that \emph{amplifies} this approximation error rather
than merely removing useful data.

\subsection{Selection Strategies}
\label{sec:strategies}

We instantiate six strategies, tagged with their access tier from
Table~\ref{tab:access}.

\paragraph{L0 / L1 baselines.}
\textsc{Random} (L0) draws $k$ nodes uniformly without replacement.
\textsc{Degree} (L1) selects the top-$k$ by node degree.
\textsc{PageRank} (L1) selects the top-$k$ by personalized PageRank
centrality. \textsc{Random} is also the \emph{architectural-baseline
probe} for the $\Delta F_{\text{arch}}$ term of
\S\ref{sec:diagnostics}; the structural baselines provide an L1
reference floor.

\paragraph{TracIn (pseudo-influence, L2-direct or L2-surrogate).}
Following~\cite{pruthi2020estimating}, we compute an influence proxy by
gradient inner-products between training and test losses:
\begin{equation}
\label{eq:tracin}
\mathrm{TracIn}(v) = \sum_{c}\eta_c\,
                     \langle\nabla_\theta\mathcal{L}(f_{\theta_c};v),\,
                            \nabla_\theta\mathcal{L}(f_{\theta_c};V_{\mathrm{val}})\rangle,
\end{equation}
where $\theta_c$ are checkpoints across training and $\eta_c$ is the
corresponding learning rate. Top-$k$ by $|\mathrm{TracIn}(v)|$. We run
TracIn on $f_\theta$ directly (L2-\textsc{direct}); the shadow-model
variant (L2-\textsc{surrogate}) is left for future work.

\paragraph{Influence Maximization (IM, L1).}
We treat the GNN's receptive field as a diffusion graph and select the $k$
nodes whose forced unlearning maximizes \emph{reachable} downstream-test
disturbance, estimated via Monte-Carlo simulation under an
independent-cascade model with edge-weight $p_{uv}=1/\deg(v)$. Following
CELF++~\cite{goyal2011celf++} we use lazy submodular evaluation
(\textsc{batch-CELF}, our v4 implementation, \S\ref{sec:experiment}).
Crucially, IM is \emph{model-free}: the IC simulation depends only on
$G$ and degree, so IM sits at L1 alongside \textsc{Degree} and
\textsc{PageRank} despite its computational sophistication. The
Monte-Carlo random seed is \emph{decoupled} from the GNN training seed
(\texttt{im\_selector\_seed=2024}) so that selection is deterministic
across the GNN seeds we evaluate (selector-Jaccard $=$ 1.0 across
seeds; \S\ref{app:imseed}).

\paragraph{Hybrid IF$+$IM (L2, bottlenecked by TracIn).}
We rank candidates by
\begin{equation}
\label{eq:hybrid}
\mathrm{Score}_\alpha(v)
 = \alpha\,\widetilde{\mathrm{TracIn}}(v) + (1-\alpha)\,\widetilde{\mathrm{IM}}(v),
\end{equation}
where $\sim$ denotes min-max normalization. \textbf{We treat $\alpha$ as a
mixing parameter, not a hyperparameter.} The endpoints $\alpha=1$
(TracIn-only, gradient-signal axis) and $\alpha=0$ (IM-only,
structural-spread axis) define the basis axes of the
\emph{Vulnerability Fingerprint} of \S\ref{sec:results-fingerprint}; the
interior $\alpha\in(0,1)$ traces the path between fingerprint endpoints,
and its curve $f(\alpha)$ is the \emph{synergy diagnostic} reported in
\S\ref{app:alpha}. We use $\alpha=0.5$ in the main matrix; the full sweep
is in Appendix~\ref{app:alpha}.

\subsection{Collateral Diagnostics}
\label{sec:diagnostics}

We position the diagnostics below as a paper contribution rather than
standard evaluation: F1 drop alone conflates targeted forgetting with
approximation-error spillover, and conflates attack-specific signal with
the architectural F1 shift caused by deleting any small set.

\paragraph{F1-shift decomposition.}
For any deletion set $S$ of size $k$, write
\begin{equation}
\label{eq:fshift}
\Delta F_{\text{total}}(S)
 \;=\; \Delta F_{\text{arch}}(k) \;+\; \Delta F_{\text{attack}}(S),
\end{equation}
where
$\Delta F_{\text{total}}(S) = F_1(\mathcal{U}(f_\theta,\cdot,S);V_{\text{te}})
- F_1(f_\theta;V_{\text{te}})$ is the observed F1 shift after
attack-driven unlearning;
$\Delta F_{\text{arch}}(k)
= \mathbb{E}_{R\sim\mathrm{Unif}(\mathcal{D}_{\text{tr}},k)}[\Delta F_{\text{total}}(R)]$
is the \emph{architectural} term, the expected F1 shift when any
uniformly-random set of size $k$ is unlearned (method-specific,
seed-stable in expectation); and $\Delta F_{\text{attack}}(S)
= \Delta F_{\text{total}}(S) - \Delta F_{\text{arch}}(k)$ is the
\emph{attack-specific} term, estimated as the paired effect (strategy F1
minus same-seed random F1). The decomposition surfaces two distinct
findings:
$\Delta F_{\text{arch}}$ varies across methods even at zero attack
signal---most methods yield $\approx 0$, but \emph{partition methods
exhibit $\Delta F_{\text{arch}}<0$} (Shard Protection,
\S\ref{sec:results-shard});
$\Delta F_{\text{attack}}$ is what our attack toolkit induces above the
architectural baseline, and is the quantity plotted in the
Vulnerability Fingerprint of \S\ref{sec:results-fingerprint}.
Reporting both terms separately is what allows us to attribute Shard
Protection cleanly to the architectural term, not to the attack.

\paragraph{Retrain gap.} Let $f^{\mathrm{R}}$ be the model retrained from
scratch on $\mathcal{D}_{\mathrm{tr}}\setminus S$ and $f^{\mathrm{U}}$ be
the unlearned model. The retrain gap is
$\mathrm{Gap}(S) = L(f^{\mathrm{R}};V_{\mathrm{te}}) - L(f^{\mathrm{U}};V_{\mathrm{te}})$.
A large gap indicates that performance loss is due to approximation
error, not data informativeness.

\paragraph{Prediction shift.} The fraction of non-target nodes whose
predicted label changes between $f_\theta$ and $f^{\mathrm{U}}$:
$\mathrm{Shift}(S) = |V_{\mathrm{te}}\setminus S|^{-1}
\sum_{v\in V_{\mathrm{te}}\setminus S}
\mathbb{1}[f^{\mathrm{U}}(v)\neq f_\theta(v)]$.

\paragraph{Hop-distance decay.}
For each retained node $v\notin S$, let $h(v)=\min_{u\in S}d_G(v,u)$
be the shortest-path graph distance to the nearest deleted node. We
report \emph{flip rate per hop bucket}: the fraction of nodes in each
bucket whose predicted class differs between the unlearned model
$f^{\mathrm{U}}$ and the exact-retrain model $f^{\mathrm{R}}$ on
$\mathcal{D}_{\mathrm{tr}}\setminus S$:
\begin{equation}
\label{eq:hopflip}
\mathrm{Flip}(h) = \frac{1}{|B_h|}\sum_{v\in B_h}\mathbb{1}\bigl[f^{\mathrm{U}}(v)\neq f^{\mathrm{R}}(v)\bigr],
\qquad
B_h = \{v\notin S : h(v)\in\text{bucket } h\}.
\end{equation}
The retrain model serves as the oracle, so $\mathrm{Flip}(h)$ isolates
the unlearning algorithm's \emph{approximation drift} from any
data-loss effect (a node where retrain itself errs does not count
unless the unlearned model differs from retrain). To make the buckets
comparable across backbones, we bin by the GCN's effective receptive
field rather than absolute hop count: \textbf{within-RF}
($h\le L$), \textbf{boundary} ($h=L+1$), and \textbf{outside-RF}
($h>L+1$), where $L$ is the number of message-passing layers. A method
whose flip rate decays sharply outside the receptive field
\emph{localizes} deletion (typical of partition and Newton-step
methods); one whose flip rate stays uniform across buckets
\emph{propagates} approximation error beyond the GCN's nominal range
(typical of objective-perturbation methods, \S\ref{sec:results-hop}).
This composition---paired-vs-retrain reporting plus hop-distance
stratification---is, to our knowledge, not in prior GU evaluation; we
treat it as a reporting protocol rather than a novel statistic, since
both components are individually standard.
