\section{Experimental Setup}
\label{sec:experiment}

\paragraph{Datasets and backbones.}
We evaluate on three node-classification benchmarks:
Cora (2{,}708 nodes / 5{,}429 edges, 7 classes),
Citeseer (3{,}327 / 4{,}732, 6 classes), and
ogbn-arxiv~\cite{hu2020open} (169{,}343 / 1.16M, 40 classes), spanning
small to large scale. We use two GNN backbones: GCN~\cite{kipf2017semi}
(2 layers, hidden 64 on Cora/Citeseer; 3 layers, hidden 256 on
ogbn-arxiv) and GAT~\cite{velickovic2018graph} (8 heads). All results
report node classification F1 on standard held-out test splits.

\paragraph{Unlearning methods.}
We benchmark \textbf{six} representative methods covering three of the
four upstream OpenGU categories with \emph{intra-family pairs} in each
covered category:
\textbf{Partition-based:} \textbf{GraphEraser}~\cite{chen2022graph}
(canonical) + \textbf{GraphRevoker} (efficient partial retraining---both
legitimate partition methods, neither pre-labeled outlier).
\textbf{IF-based:} \textbf{GIF}~\cite{wu2023gif} (canonical, single Newton
step) + \textbf{IDEA}~\cite{dong2024idea} (certified-gradient, predicted
intra-family outlier).
\textbf{Learning-based:} \textbf{GNNDelete}~\cite{cheng2023gnndelete}
(canonical, deletion-aware proximal objective) +
\textbf{MEGU}~\cite{li2024towards} (mutual-evolution, predicted
intra-family outlier).
The fourth OpenGU category (Others: UtU, Projector at deployment time) is
out of scope; GST and GUKD are listed as future-work 3rd members and
fallbacks for the feasibility gate (\S\ref{sec:limitations}).

\paragraph{Attack budget and seeds.}
The main matrix uses small-budget regime $r=0.05$ (5\% of training
nodes), with 5 seeds (\texttt{42, 212, 722, 1337, 2024}) on
Cora/Citeseer and 3 seeds on ogbn-arxiv (compute budget; see
\S\ref{sec:setup-arxiv}). The IM Monte-Carlo seed is fixed at
\texttt{2024} across all GNN seeds (\S\ref{sec:strategies}); we verified
selector Jaccard $=1.0$ between seeds in a controlled micro-test
(\S\ref{app:imseed}). The deletion-ratio sweep
$r\in\{0.01,0.05,0.10,0.20\}$ on Cora/GCN appears in
Appendix~\ref{app:ratio}.

\paragraph{Reporting protocol.}
Following the decomposition in \S\ref{sec:diagnostics}, we report
(a)~\emph{paired effect}---per-seed F1 difference between an attack
strategy and the matched random baseline (random uses the same GNN
seed)---with paired mean, paired standard deviation, 95\% bootstrap CI,
and a one-sided $t$-test against the null $\mu\le 0$;
(b)~retrain gap, prediction shift, and hop-distance decay
(\S\ref{sec:diagnostics});
(c)~MIA AUC using the shadow-model attack
of~\cite{olatunji2021membership}.
The architectural term $\Delta F_{\text{arch}}(k)$ is reported separately
as a per-method bar chart in \S\ref{sec:results-shard}.

\paragraph{Implementation.}
All methods are implemented in PyTorch~\cite{paszke2019pytorch} +
PyTorch~Geometric~\cite{fey2019fast}. Training uses Adam with learning
rate $10^{-2}$, weight decay $5\times10^{-4}$, 100 epochs on
Cora/Citeseer (200 on ogbn-arxiv). The IM selector uses our
\textsc{batch-CELF} variant with candidate fraction 0.1 (top-degree
pruning) and 50 Monte-Carlo rounds, achieving \interim{34$\times$}
speed-up over brute-force CELF with $<2\%$ spread loss
(\S\ref{app:imhp}). Source code and configurations will be released upon
acceptance.

\subsection{Scaling to ogbn-arxiv}
\label{sec:setup-arxiv}

ogbn-arxiv (169K nodes) requires three deviations from the
small-graph protocol. (i)~\textbf{3 seeds, not 5}---the per-cell
GPU-h cost is roughly $30\times$ the Cora cost; we report per-cell paired
CI widths to make the resulting reduction in statistical power explicit.
(ii)~\textbf{TracIn G-matrix at 169K nodes} requires either chunked
gradient accumulation or a candidate-subsampling probe; we use chunked
accumulation on an 80~GB GPU. The Physics dataset's higher feature
dimension was found infeasible with the same protocol and is out of
scope (\S\ref{sec:limitations}). (iii)~\textbf{IM candidate-fraction at
scale} is held at 0.1 to keep batch-CELF tractable; this cuts the
candidate set from $\sim$90K to $\sim$9K and is validated at small scale
in \S\ref{app:imhp}. (iv)~The arxiv GCN uses 3 layers / hidden 256;
hop-decay buckets in \S\ref{sec:results-hop} are reported relative to
the GCN's effective receptive field rather than absolute hop count.
