\section{Discussion and Conclusion}
\label{sec:conclusion}

\subsection{Summary}
We presented the first systematic adversarial audit of approximate
graph unlearning. By treating deletion-set selection as the attacker's
primary degree of freedom, we exposed a 2D \emph{Vulnerability
Fingerprint} on which mechanism family is the dominant predictor and
within-family mechanism choice is a strong modulator. Learning-based
GNNDelete collapses under tiny deletion budgets; IF-based GIF shows a
small, Newton-step-bounded effect; the Partition pair (GraphEraser,
GraphRevoker) exhibits a counterintuitive \emph{Shard Protection
Effect}, formally an architectural F1-shift term that no selector can
amplify; and within-family outliers MEGU (Learning-based) and IDEA
(IF-based) resist all six selectors despite belonging to vulnerable
parent categories.

\subsection{Intra-Family Outliers as Within-Family Heterogeneity}
\label{sec:disc-outliers}

MEGU and IDEA are not a separate ``robust family''---they belong to
\emph{different} parent categories under the OpenGU taxonomy
(Learning-based and IF-based respectively). What unifies them is
geometric: both sit far from their parent-category centroids in the
Vulnerability Fingerprint, near the origin.
The mechanism reading is that mutual-evolution (MEGU) and
certified-gradient (IDEA) are \emph{intra-category alternatives} whose
specific design decouples from the loss-gradient signal that TracIn and
IM exploit, even though their family-mates GNNDelete and GIF do not
exhibit this decoupling.

We frame this as an honest joint statement: it is partly a robustness
property of the specific design and partly an evaluation gap of the
current attacker class. A natural next step is to design selectors
that target the specific algebraic structure of MI-regularised or
certified-gradient unlearners; whether GUKD (Learning, distillation) or
CGU (IF, certified) also sit at the origin would test whether the
within-family decoupling we observe is a meta-property orthogonal to
the official taxonomy.

\subsection{Limitations}
\label{sec:limitations}

\textbf{L1.} GraphEraser's shard-count is partially swept (\S\ref{app:shard});
exhaustive ablation is left to future work.
\textbf{L2.} ogbn-arxiv runs use 3 seeds rather than 5; we report
per-cell paired CI widths to make the resulting power tradeoff explicit.
\textbf{L3.} TracIn's $G$-matrix does not scale to feature dimension
$\gtrsim 8$K (Physics dataset out of scope); the chunked accumulation
that fits ogbn-arxiv on an 80~GB GPU does not generalise.
\textbf{L4.} The L2 numbers reported in \S\ref{sec:results-fingerprint}
are L2-\textsc{direct} (production weights known), an \emph{upper
bound} on the realistic L2-\textsc{surrogate} attacker who trains a
shadow model from the public protocol and transfers the deletion set
(Table~\ref{tab:access}). The transferability gap between the two is
selector- and architecture-dependent; we do not characterise it
quantitatively in this work and leave the surrogate sweep as future
work. White-box (L3) attackers who modify training data or the
unlearning algorithm itself remain out of scope.
\textbf{L5.} The deletion-ratio sweep (\S\ref{app:ratio}) characterises
budget elasticity on Cora/GCN at $r\in\{0.01,0.05,0.10,0.20\}$; the
arxiv ratio sweep is left to future work.
\textbf{L6.} We cover three of four OpenGU categories with intra-family
pairs in each; the ``Others'' category (UtU, Projector at deployment
time) and 3rd-member within-family extensions (e.g., GST as 3rd IF,
GUKD as 3rd Learning) are listed as future work.
\textbf{L7 (visualization scope).} The experimental design spans seven
axes (method, dataset, backbone, strategy, seed, ratio, hybrid mixing
$\alpha$), well beyond what any single visualisation can render
honestly. We report results via section-conditional slicing---fixing a
subset of axes per claim and varying only the axes germane to that
claim---rather than a unified low-dimensional projection. Cross-cell
generalisations rely on inductive consistency across tested slices,
not on Cartesian-complete coverage. Untested combinations---notably
citeseer/GAT, arxiv/GAT, the joint $\alpha\times r$ grid, and strategy
sweeps at non-default ratios---are explicitly out of scope. We chose
this conditioning approach over dimensionality reduction (PCA, UMAP) to
preserve the physical meaning of the fingerprint axes, at the cost of
requiring readers to integrate across multiple figures.

\subsection{Broader Impact}
\label{sec:broader}

Our results argue that any future approximate GU method should report
not only retrain-time speedup and random-deletion utility but also a
worst-case adversarial-deletion bound. The diagnostic kit we
introduce---$\Delta F$-decomposition, retrain gap, prediction shift,
hop-distance decay---is independent of our specific selectors and can
be reused with arbitrary attacks. We believe this aligns the GU
community with the robustness-evaluation norms of adversarial machine
learning more broadly.

\paragraph{What the realistic threat looks like.}
A coalition-of-users on a deletion-API platform reaches the L1 tier of
Table~\ref{tab:access} for free---public graph, reconstructed training
mask, no model access required. Our IM-axis numbers therefore describe
a threat that is \emph{always available}, not a hypothetical
permission level. The L2-direct TracIn numbers we report further serve
as upper bounds on what such a coalition can reach by training a
shadow model on the (commonly disclosed) training protocol, with the
transferability gap setting the actual realised harm. The most
operationally important takeaway is therefore the IM-axis position of
each method: GNNDelete already collapses at L1, where the access
barrier is zero.

The Shard Protection Effect is dual-use: the same architectural
property that bounds an adversary's utility-collapse could also mask
malicious unlearning requests issued under ordinary deletion-API
traffic. We therefore frame Shard Protection as a defensive
\emph{insight}, not a deployment recommendation, and direct
deletion-API platform operators to the responsible-disclosure note in
the supplementary material. We do not release attack-tuned model
checkpoints, only the methodology and code.

\subsection{Future Directions}
Three problems stand out.
(1)~\emph{Mechanism-aware selectors:} a selector that targets MEGU's
mutual-evolution objective or IDEA's certified projection would test
whether the within-family outlier behavior we observe is a true
property or a selector artifact.
(2)~\emph{Defenses:} the Shard Protection Effect suggests that
partition-based aggregation may be a principled defense; quantifying
the privacy-vs-robustness trade-off of shard-based GU is the natural
follow-up, with the MIA decoupling of \S\ref{sec:results-mia} as a
starting point.
(3)~\emph{Beyond utility:} our attacks target downstream F1; analogous
attacks targeting privacy leakage (e.g., MIA AUC reduction
\emph{after} unlearning) would close the threat-model loop.
