\section{Implementation Details}
\label{app:impl}

\subsection{GNN Message Passing Primer}
\label{app:gnn-primer}
For completeness, we recall the message-passing form used by the GNN
backbones in this paper. Let $h_v^{(0)}=x_v$ be the feature vector of
node $v$. An $L$-layer GNN updates node representations by aggregating
messages from the graph neighborhood,
\begin{equation}
h_v^{(\ell+1)}
= \phi_\ell\!\left(h_v^{(\ell)},
  \operatorname{AGG}_{u\in\mathcal{N}(v)}
  \psi_\ell(h_v^{(\ell)},h_u^{(\ell)},e_{uv})\right),
\qquad \ell=0,\ldots,L-1,
\end{equation}
and predicts from $h_v^{(L)}$. Thus a deletion request is not an
i.i.d.\ sample removal: deleting a node removes its own training loss
and changes the message-passing context of retained neighbors. Exact
retraining can re-optimize under this modified graph, while approximate
unlearning must update from the original parameters. This is why our
diagnostics separate the effect of data removal from approximation drift
and report hop-distance decay relative to the GNN receptive field.

\subsection{IM Selector: Batched CELF}
We adopt CELF++~\cite{goyal2011celf++} with two modifications:
(a)~candidate-set pruning to the top-degree decile of the training set
(\texttt{candidate\_fraction=0.1}) before MC simulation, reducing the
search space by $\sim$10$\times$ on ogbn-arxiv with negligible spread loss;
(b)~a \emph{decoupled} Monte-Carlo seed
(\texttt{im\_selector\_seed}, default 2024) that is independent of the
GNN training seed, so that the selected node set is identical across the
five GNN seeds. The hyperparameter sweep is in
Appendix~\ref{app:imhp}; the selector-seed sanity test is in
Appendix~\ref{app:imseed}.

\subsection{TracIn for GNNs}
For node classification we treat the per-node training loss as
$\mathcal{L}_v = \mathrm{CE}(f_\theta(v), y_v)$ and the validation loss
as the mean over $V_{\mathrm{val}}$. We average gradients across 5
evenly spaced checkpoints (epochs 20, 40, 60, 80, 100) and weight by
the checkpoint learning rate.

\subsection{Compute Resources}
Cora and Citeseer experiments fit on a single 4090 (24~GB); ogbn-arxiv
runs on an 80~GB H800 with batch size 256 and uses up to
${\sim}22$~GB peak GPU memory for the collateral retrain pass.
Total compute for the full Phase~B matrix (${\sim}1{,}500$ cells
across 4 configs) is approximately $14$--$30$~GPU-hours on the 4090
plus ${\sim}12$~GPU-hours on the H800.

\section{Additional Results}
\label{app:results}

This appendix collects per-cell tables, hop-decay curves per family,
and ogbn-arxiv feasibility commentary. The full per-cell aggregate
CSV (360 rows: 6 methods $\times$ 6 strategies $\times$ 5 seeds
$\times$ \{Cora/GCN, Cora/GAT\}, $r{=}0.05$) is shipped with the
release.

\subsection{1D Vulnerability Spectrum (Marginal Projection)}
\label{app:results-1d}
A 1D bar chart over methods using the $\ell_2$ norm of the
$(\Delta F^{\text{attack}}_{\mathrm{IM}},
\Delta F^{\text{attack}}_{\mathrm{TracIn}})$ fingerprint coordinate
preserves the prior ``vulnerability spectrum'' framing for warm-up
readers; the canonical ranking on Cora/GCN is GNNDelete $\gg$ GIF
$>$ MEGU $>$ IDEA $>$ GraphRevoker $\approx$ GraphEraser.

\subsection{Per-Cell Effect Tables}
The full method $\times$ strategy $\times$ seed effect tables for
Cora/GCN and Cora/GAT, and the ogbn-arxiv summary (3-seed feasible
subset), are reported in the supplementary aggregate
(\texttt{results/\_phase\_b\_aggregate.csv}).

\subsection{Hop-Distance Decay Curves}
On Cora/GCN ($L{=}2$) under TracIn-based deletion, GIF and IDEA
flips are sharply concentrated within the 1-hop receptive field
(${\approx}7\%$ flip rate at $h{=}1$, ${<}0.3\%$ at $h{\ge}2$);
GNNDelete is far more diffuse (${\approx}48\%$ at $h{=}1$,
${\approx}18\%$ at $h{=}2$, $4.5\%$ at $h{=}3$). The Partition pair
shows broad flips across all hop buckets ($35$--$40\%$ at $h{=}1$,
$20\%$+ even at $h{>}3$), consistent with shard re-training rather
than localised approximation drift.

\section{Ablation: IM Selector Seed Decoupling}
\label{app:imseed}

\textbf{Purpose.} Validate that the Vulnerability Fingerprint and
$\alpha$-sweep findings are not artefacts of selector noise.
Table~\ref{tab:jaccard} reports selection-set Jaccard before and after
the seed-decoupling fix.

\begin{table}[h]
\centering
\small
\caption{\textbf{Selection-set Jaccard across 5 GNN seeds, before vs.\
after the IM selector-seed decoupling fix.} Cora/GCN/$r{=}0.05$.}
\label{tab:jaccard}
\begin{tabular}{@{}lrr@{}}
\toprule
Strategy & Pre-fix (coupled) & Post-fix (decoupled) \\
\midrule
\textsc{Random}    & $0.023$ & $0.023$ \\
\textsc{Degree}    & $1.000$ & $1.000$ \\
\textsc{PageRank}  & $1.000$ & $1.000$ \\
\textsc{TracIn}    & $0.415$ & $0.415$ \\
\textsc{IM}        & $0.129$ & $\mathbf{1.000}$ \\
\textsc{Hybrid}    & $0.646$ & $0.917$ \\
\bottomrule
\end{tabular}
\end{table}

After the fix, the paired-effect 95\% CI width on the GNNDelete IM
cell is $\pm 9.99\%$ ($N{=}5$, two-sided $t$-CI), reflecting the
inherently high seed-to-seed variance of GNNDelete's collapse mode
rather than selector-induced jitter.

\section{Ablation: GraphEraser Shard Configuration}
\label{app:shard}

\textbf{Purpose.} Lock down Shard Protection
(\S\ref{sec:results-shard}) as a mechanism-driven property rather than
a hyperparameter coincidence. We sweep shard counts
$C\in\{5,10,20\}$ on Cora/GCN/$r{=}0.05$ with strategies
$\{\textsc{Random},\textsc{IM},\textsc{Hybrid}\}$ and 5 seeds. The
paired effect remains ${\le}0$ across all shard counts; the
noise-floor term $\Delta F_{\text{noise}}$ stays negative
($-5\%$ to $-15\%$ on Cora), confirming Shard Protection is robust to
the partition-count hyperparameter.

\section{Ablation: \texorpdfstring{$\alpha$}{alpha}-Sweep as Synergy Diagnostic}
\label{app:alpha}

\textbf{Purpose.} We treat $f(\alpha)\!:=\!\Delta F^{\text{attack}}$ of
the Hybrid score (Eq.~\ref{eq:hybrid}) as a synergy diagnostic; the
curve shape encodes how IM and TracIn signals interact per family.
Curve readings: linear $\Rightarrow$ independent additive selection;
concave (above chord) $\Rightarrow$ \emph{synergy}; convex (below
chord) $\Rightarrow$ \emph{redundancy}; flat at zero $\Rightarrow$
mechanism-incomparable.

\textbf{Design.} 5 $\alpha$ values $\{0.0, 0.25, 0.5, 0.75, 1.0\}$,
6 methods, 2 cells (Cora/GCN, Cora/GAT), 5 seeds; the endpoints
$\alpha\in\{0,1\}$ are reused from the main matrix. Total new runs
$N{=}180$. The full $\alpha$-sweep grid is deferred to a
supplementary release; the $\alpha{=}0.5$ column appears in the main
fingerprint as the ``hybrid'' strategy.

\section{Ablation: IM Hyperparameters}
\label{app:imhp}

\textbf{Purpose.} Defend the ``${\sim}10\times$ speedup with
$<$2\% spread loss'' claim of \S\ref{sec:experiment} and the IM
scaling story of \S\ref{sec:setup-arxiv}. We sweep candidate-fraction
$\in\{0.05,0.1,0.2\}$ and MC rounds $\in\{25,50,100\}$ on
Cora/GCN/GIF/$r{=}0.05$, reporting paired effect, selection-set
Jaccard with full-CELF reference, and wall-clock. The full robustness
grid is shipped with the supplement; the canonical setting
(\texttt{candidate\_fraction}${=}0.1$, $50$ MC rounds) maintains
$\mathrm{Jaccard}{>}0.95$ against full-CELF on the same seed while
incurring $<2\%$ spread loss.

\section{Ablation: Deletion Ratio Sweep}
\label{app:ratio}

\textbf{Purpose.} Characterise per-family budget elasticity, removing
the ``$r{=}0.05$ only'' restriction.

\textbf{Design.} $r\in\{0.01,0.05,0.10,0.20\}$, all 6 methods,
strategies $\{\textsc{Random}, \textsc{IM}, \textsc{TracIn}\}$,
Cora/GCN, 5 seeds. Total $N{=}360$ runs.

\textbf{Reading guide.} A 4-panel grid (one per family) reads as
follows: linear in $r$ $\Rightarrow$ effect proportional to budget
(predicted: GIF); sub-linear $\Rightarrow$ bounded approximation;
negative or flat $\Rightarrow$ Shard Protection / null effect
persists; a threshold (knee) $\Rightarrow$ critical $r^*$ where the
mechanism breaks. The ratio sweep is reported in the supplementary
release; on the main matrix at $r{=}0.05$, Shard Protection persists
on the Partition pair and GNNDelete remains the dominant collapse
mode.

\section{Per-Method Hyperparameters}
\label{app:hyperparams}
We adopt the published defaults from each method's original paper
where specified, and our reproduced defaults (matching the OpenGU
benchmark) where not. The full per-method hyperparameter table is
included with the released configuration files
(\texttt{model/properties/}).

\section{Negative and Boundary-Case Analyses}
\label{app:negative}

\paragraph{Cases where attacks underperform random.}
On the partition pair (GraphEraser, GraphRevoker), all model-coupled
selectors yield smaller F1 gain than random---the Shard Protection
upper-bound (\S\ref{sec:results-shard}). The mechanism: adversarial
nodes concentrate in fewer shards than random selection, leading to
weaker aggregator disturbance; per-shard diagnostics confirming this
concentration are included in the supplementary release.
